\documentclass[12pt]{article}

% Formatting required by the proposal guideline
\usepackage[margin=1in]{geometry}
\IfFileExists{newtxtext.sty}{
    \usepackage{newtxtext,newtxmath} % Times-style text and mathematics
}{
    \usepackage{mathptmx}            % Fallback Times-style package
}
\usepackage{setspace}
\usepackage{cite}                % Compressed numerical citations
\usepackage[hidelinks]{hyperref}

\doublespacing
\setlength{\parindent}{0.5in}
\setlength{\parskip}{0pt}

\begin{document}

\begin{center}
    {\large\bfseries A One-Dimensional Potential-Barrier Model for Quantum Tunneling of MOSFET Gate-Leakage}
\end{center}

Quantum tunneling occurs when a particle with energy \(E<V_0\) has a nonzero probability of being found beyond a finite potential barrier, because its wavefunction decays exponentially rather than becoming immediately zero within the barrier \cite{townsend2010}. MOSFETs are electronic switches used in integrated circuits. The gate controls the conductivity of a silicon channel through an electric field across a thin oxide layer. In a simplified one-dimensional model, the oxide thickness \(t_{\mathrm{ox}}\) corresponds to the barrier width \(a\). If the particle energy and barrier height are held constant, reducing \(t_{\mathrm{ox}}\) shortens the physical distance over which the wavefunction decays. The wavefunction therefore has a larger amplitude at the far side of the oxide, increasing the tunneling probability and gate leakage. Greater gate leakage can increase standby power consumption and heat dissipation, and can even reduce device reliability \cite{green2001review}.

The research question is: To what extent is the experimentally measured dependence of gate leakage current density on oxide thickness consistent with the prediction of a one-dimensional rectangular potential barrier model in MOSFETs? This study will investigate how \(J_G\) changes with \(t_{\mathrm{ox}}\) at a fixed gate voltage of \(V_G=1.5~\mathrm{V}\). In the theoretical model, \(t_{\mathrm{ox}}\) will be treated as the barrier width, while the particle energy and barrier height will be held constant, and the tunneling probability \(T\) will be calculated in MATLAB. Experimental \(J_G\)-against-\(t_{\mathrm{ox}}\) data will be extracted from Green et al.'s published plot of NMOSFET measurements with transmission-electron-microscopy-measured oxide thicknesses \cite{green1999limits,green2001review}. A graph digitizer will be used to extract the data. The relationships \(\ln T\) against \(t_{\mathrm{ox}}\) and \(\ln J_G\) against \(t_{\mathrm{ox}}\) will be plotted separately, and their slopes and overall trends will be compared. Significant deviations among trends may represent limitations of the model because in a real MOSFET the electric field can tilt the oxide barrier, which may vary with oxide thickness under a fixed gate voltage \cite{green2001review}.

\newpage
\IfFileExists{IEEEtran.bst}{\bibliographystyle{IEEEtran}}{\bibliographystyle{unsrt}}
\bibliography{references}

\end{document}
